My Past Work

### 2025-01-28 index.qmd
Update for Mobile

.tiktok-container {
  display: flex;
  flex-wrap: wrap;
  justify-content: center;
  width: 105%; 
}

.tiktok-embed {
  box-sizing: border-box;
  max-width: 100%;
  flex: 1 1 300px;
  margin: 0 auto; 
}

@media screen and (max-width: 600px) {
  .tiktok-embed {
    min-width: auto;
  }
}
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161" style="max-width: 605px;min-width: 325px;">

@@

<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168" style="max-width: 605px;min-width: 325px;">

@@

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
:::

## Contact Details

>>>>

  .tiktok-container {
    display: flex;
    flex-wrap: wrap;
    justify-content: space-between; /* Distribute space between items */
    gap: 20px; /* Add spacing between items */
    width: 100%;
    max-width: 1200px; /* Limit maximum width for larger screens */
    margin: 0 auto; /* Center the container */
  }

  .tiktok-embed {
    box-sizing: border-box;
    flex: 1 1 calc(50% - 10px); /* Two items per row with spacing */
    max-width: calc(50% - 10px); /* Two items per row with spacing */
    min-width: 300px; /* Minimum width for each embed */
  }

  @media screen and (max-width: 600px) {
    .tiktok-embed {
      flex: 1 1 100%; /* Full width on mobile */
      max-width: 100%; /* Full width on mobile */
    }
  }
</style>
```
::: tiktok-container
<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7181240142063996161" data-video-id="7181240142063996161">

@@

<blockquote class="tiktok-embed" cite="https://www.tiktok.com/@mentaikofries_/video/7383243879715196168" data-video-id="7383243879715196168">

@@

</blockquote>
:::

```{=html}
<script async src="https://www.tiktok.com/embed.js"></script>
```
## Contact Details

### 2025-01-28 interests.qmd
Update for Mobile

### (1) SlideCraft - AI Powered Design Tool

@@

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" src="https://embed.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/Slidecraft-Hi-Fi-Prototype-Flow?page-id=0%3A1&amp;node-id=1-31&amp;starting-point-node-id=1%3A31&amp;embed-host=share">

</iframe>

### (2) GPTDashboard - Desktop View

@@

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
src="https://embed.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/ChatGPT-Dashboard-Hi-Fi-Desktop-View-Prototype-Link?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&embed-host=share" 
allowfullscreen>

</iframe>

### (3) SaveWatt

@@

<iframe style="border: 1px solid rgba(0, 0, 0, 0.1);" width="800" height="450" 
src="https://embed.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&embed-host=share" 
allowfullscreen>

</iframe>

>>>>

### (1) SlideCraft - AI Powered Design Tool - [Try](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)

@@

[![](src/images/Slidecraft.png)](https://www.figma.com/proto/4o0fMCNtIOXtFuupnMgmlU/(Slidecraft)-Hi-Fi-Prototype-Flow?page-id=0%3A1&node-id=1-31&starting-point-node-id=1%3A31&t=Mh9u0WSzDA1yIXVO-1)

### (2) GPTDashboard

@@

#### Desktop View - [Try](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)

[![](src/images/GPTDashboard.png)](https://www.figma.com/proto/LZcst4QtAgGJgik4eHhaRb/(ChatGPT-Dashboard)-Hi-Fi-Desktop-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-228&starting-point-node-id=1%3A228&t=p4qJvBRCwOvr5VdO-1)

#### Mobile View - [Try](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)

[![](src/images/Mobile Dashboard.png)](https://www.figma.com/proto/XAkmFk4Ob0sKCjq9WicOTn/(ChatGPT-Dashboard)-Hi-Fi-Mobile-View-Prototype-Link%3A?page-id=0%3A1&node-id=1-155&starting-point-node-id=1%3A155&scaling=scale-down&content-scaling=fixed&t=usOMIBXFWyw4m05r-1)

### (3) SaveWatt - [Try](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)

@@

[![](src/images/SaveWatt_Prototype.png)](https://www.figma.com/proto/33D1uDg1g786wbtU9np2gq/4_G3_Prototype?page-id=3%3A646&node-id=89-2546&starting-point-node-id=89%3A2546&t=NrbMP0AecEP9SCMu-1)
